\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-04 manuscript.Rmd
All possible plots are in ggplot2

```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200)
#options(knitr.duplicate.label = "allow")
set.seed(123)
par(family = "Arial")
```

@@

}")
export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Manuscript.figures/Flowchart1.png", dpi = 1200)

@@

```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.png')
```

# Results
```{r ggplot2, include=F}
apatheme=theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        #text=element_text(family = "Helvetica",),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
```

@@

```{r HullEFA, include=FALSE}
# HULL
EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL)+xlab("Factor Number (Hull Method)")+ylab("CAF")+ 
  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2"))+theme(legend.position = "None") 
```

@@

write.csv(full.map, "Table_raw/map_stat")
```
Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution. However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.
```{r factors, include=F}
jpeg("Manuscript.figures/factors.png", width = 400, height = 800)
cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")
```

```{r facIdFig, out.height="350%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
knitr::include_graphics("Manuscript.figures/factors.png")

@@

export_svg(EFAplot) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Manuscript.figures/EFAplot.png", dpi = 1200)

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Sup.Table \@ref(tab:MinResTab)). Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. Figure \@ref(fig:EFAplot) depicts the obtained five-five factor structure. However, the histogram of the absolute values of non-redundant residual-correlations (Sup.Figure \@ref(fig:EFAResiduals)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Sup.Table \@ref(tab:sixFacTab)).

@@

```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="60%", out.width="100%", results='asis'}
knitr::include_graphics('Manuscript.figures/EFAplot.png')

@@

```{r EFARes, message=FALSE, warning=FALSE, include=F}
jpeg("Manuscript.figures/EFAResidual.png", width = 800, height = 750)
hist(residual.5F,  main = NULL, xlab = "Residuals", ylim=c(0, 400))
abline(h =51, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)
```

@@

gt.fullTable <-  rbind( efa.gt, cfa.gt) %>% 
  gt() %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "grey",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "grey",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("**LEBA**"),
    subtitle = md("Summary Descriptives of CFA and EFA Sample (N =690)")
  ) %>% 
  tab_footnote(
    footnote = md("**Histogram**"),
    locations = cells_column_labels(columns = hist_data)
  ) %>%
  tab_footnote(
    footnote = md("**Density**"),
    locations = cells_column_labels(columns = dens_data)
  ) %>% 
#create groups of columns
tab_spanner(
  label = "Items",
  columns = Items
) %>%
  tab_spanner(
    label = "Summary Statistics",
    columns = nr:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Items = ("LEBA  Items"),
  nr = ("n"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = everything()
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Items,
    palette = "ggthemes::fivethirtyeight"
  ) %>% 
    tab_row_group(
      group = "CFA (n =262)",
     rows = 26:48

@@

```{r gtPic, echo=FALSE, out.height="100%", out.width="200%", fig.cap= ' Summary Descriptives of CFA and EFA Sample'}
knitr::include_graphics('Manuscript.figures/gt.png')

@@

## Confirmatory Factor Analysis

@@

```{r f1itminf, include=F, warning=F}

jpeg("Manuscript.figures/F1testinfo.png", width = 800, height = 750)

plot_grid(
  F1title, f1itemplot,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)

)
dev.off()
```

```{r f2iteminf, include=F, warning=F}
jpeg("Manuscript.figures/F2testinfo.png", width = 800, height = 750)
plot_grid(
  F2title, f2itemplot,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)
)
dev.off()
```

```{r f3iteminf, include=F, warning=F}
jpeg("Manuscript.figures/F3testinfo.png", width = 800, height = 750)
plot_grid(
  F3title, f3itemplot,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)
)
dev.off()
```

```{r f4iteminf, include=F, warning=F}
jpeg("Manuscript.figures/F4testinfo.png", width = 800, height = 750)
plot_grid(
  F4title, f4itemplot,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)
)
dev.off()
```

```{r f5iteminf, include=F, warning=F}
jpeg("Manuscript.figures/F5testinfo.png", width = 800, height = 750)
plot_grid(
  F5title, f5itemplot,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)
)
dev.off()
```

@@

```{r itmeinfo, eval=FALSE, fig.cap="Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, include=FALSE, out.height="60%", out.width="100%"}
knitr::include_graphics('Manuscript.figures/iteminfo.png')

@@

# Person Fit ####
## F1 Person fit ####
F1.personfit <- personfit(F1_fit) 
F1.personfit_model_misfits <- subset(F1.personfit, Zh < -2)
rownames(F1.personfit_model_misfits)
nrow(F1.personfit_model_misfits)
hist(F1.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
abline(v = -2, lwd = 2, lty = 2)
F1.person <- ggplot(F1.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F1")+apatheme

>>>>

```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200, fig.width = 6,
 fig.asp = 0.8,out.width = "80%")
#options(knitr.duplicate.label = "allow")
set.seed(123)
par(family = "Arial")
```

@@

}")
library(jpeg)
export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  writeJPEG("Manuscript.figures/Flowchart1.jpeg",bg = "white", quality = 1)

@@

```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg')
```

# Results
```{r ggplot2, include=F}
apatheme=theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        #text=element_text(family = "Helvetica"),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        plot.title = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))

@@

```{r HullEFA, include=FALSE}
# HULL
EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL)+xlab("Factor Number (Hull Method)")+ylab("CAF")+ 
  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2"))+theme(legend.position = "None")

@@

write.csv(full.map, "Table_raw/map_stat")
```
Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution. However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.
```{r factors, include=F}
fator <- cowplot::plot_grid(parallel, scree.plot,Hull, 
                   labels = "AUTO",
                   ncol=1, 
                  align = "v", 
                  label_size = 12,
                  label_fontfamily = "serif",
                  label_fontface = "plain")
ggsave("Manuscript.figures/factors.png",fator, width = 6, height = 12, dpi = 600)
```

```{r facIdFig, out.height="100%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}

knitr::include_graphics('Manuscript.figures/factors.png')

@@

export_svg(EFAplot) %>%
  charToRaw() %>%
  rsvg() %>%
  writeJPEG("Manuscript.figures/EFAplot.jpeg",bg = "white", quality = 1)

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Sup.Table \@ref(tab:MinResTab)). Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. Figure \@ref(fig:EFAplot)(A) depicts the obtained five factor structure. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:EFAplot)(B)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Sup.Table \@ref(tab:sixFacTab)).

@@

@@

```{r EFARes, message=FALSE, warning=FALSE, include=F}
#hist(residual.5F,  main = NULL, xlab = "Residuals", ylim=c(0, 400))
#abline(h =51, lwd = 2, lty = 2)
#abline(v =.05,lwd = 2, lty = 2)
res.dat <- as.data.frame(unclass(residual.5F))
residual.data <- as.data.frame(gather(res.dat, Items, Residuals))

residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill=I("grey")) + xlim(-.2,.2)+ ylim(0,250)+apatheme +geom_vline(xintercept = .05)+
  labs( y="Frequency")

```{r EFAplotprep, include=F}
library(jpeg)
library(png)
library(cowplot)

img1 <- readJPEG("Manuscript.figures/EFAplot.jpeg")

p1 <- ggplot2::ggplot() + ggplot2::annotation_custom(grid::rasterGrob(img1,
                                                                      width=NULL,
                                                                      height=NULL),
                                                     -Inf, Inf, -Inf, Inf)+apatheme

EFAplot.1 <- plot_grid(
 p1, residual.plot,
  labels = "AUTO",
  align="h",
  ncol = 2,
  label_size = 12,
  label_fontfamily = "serif",
  label_fontface = "plain",
  label_y = .98,
  label_x = .04
)

```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis (B) Histogram of nonredundent residula correlations', warning=FALSE, out.height="80%", out.width="100%", results='asis'}
EFAplot.1

@@

```{r efagt,include=F}
efa.gt %>% 
gt() %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "grey",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "grey",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("**LEBA**"),
    subtitle = md("Summary Descriptives EFA Sample (N =428)")
  ) %>% 
  tab_footnote(
    footnote = md("**Histogram**"),
    locations = cells_column_labels(columns = hist_data)
  ) %>%
  tab_footnote(
    footnote = md("**Density**"),
    locations = cells_column_labels(columns = dens_data)
  ) %>% 
#create groups of columns
tab_spanner(
  label = "Items",
  columns = Items
) %>%
  tab_spanner(
    label = "Summary Statistics",
    columns = nr:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Items = ("LEBA  Items"),
  nr = ("n"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = everything()
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Items,
    palette = "ggthemes::fivethirtyeight") %>% 
  gtsave("Manuscript.figures/efagt.png",vwidth = 7000)

```{r cfagt,include=F}
cfa.gt %>% 
gt() %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "grey",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "grey",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("**LEBA**"),
    subtitle = md("Summary Descriptives CFA Sample (N =262)")
  ) %>% 
  tab_footnote(
    footnote = md("**Histogram**"),
    locations = cells_column_labels(columns = hist_data)
  ) %>%
  tab_footnote(
    footnote = md("**Density**"),
    locations = cells_column_labels(columns = dens_data)
  ) %>% 
#create groups of columns
tab_spanner(
  label = "Items",
  columns = Items
) %>%
  tab_spanner(
    label = "Summary Statistics",
    columns = nr:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Items = ("LEBA Items"),
  nr = ("n"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = everything()
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Items,
    palette = "ggthemes::fivethirtyeight") %>% 
  gtsave("Manuscript.figures/cfagt.png",vwidth = 7000)

```{r eval=FALSE, include=FALSE}
gt.fullTable <-  rbind( efa.gt, cfa.gt) %>% 
  gt() %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "grey",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "grey",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("**LEBA**"),
    subtitle = md("Summary Descriptives of CFA and EFA Sample (N =690)")
  ) %>% 
  tab_footnote(
    footnote = md("**Histogram**"),
    locations = cells_column_labels(columns = hist_data)
  ) %>%
  tab_footnote(
    footnote = md("**Density**"),
    locations = cells_column_labels(columns = dens_data)
  ) %>% 
#create groups of columns
tab_spanner(
  label = "Items",
  columns = Items
) %>%
  tab_spanner(
    label = "Summary Statistics",
    columns = nr:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Items = ("LEBA  Items"),
  nr = ("n"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = everything()
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Items,
    palette = "ggthemes::fivethirtyeight"
  ) %>% 
    tab_row_group(
      group = "CFA (n =262)",
     rows = 26:48

@@

```{r efagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives EFA Sample'}
knitr::include_graphics('Manuscript.figures/efagt.png')

@@

```{r cfagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives of CFA Sample'}
knitr::include_graphics('Manuscript.figures/cfagt.png')

```
## Confirmatory Factor Analysis

@@

```{r iteminfoggplot3, include=F}
Theta <- matrix(seq(-6,6, by = .1))

##Item Extraction
F1.item1 <- extract.item(F1_fit, 1)#item number
F1.item2 <- extract.item(F1_fit, 2)
F1.item3 <- extract.item(F1_fit, 3)
F2.item1 <- extract.item(F2_fit, 1)
F2.item2 <- extract.item(F2_fit, 2)
F2.item3 <- extract.item(F2_fit, 3)
F2.item4 <- extract.item(F2_fit, 4)
F2.item5 <- extract.item(F2_fit, 5)
F2.item6 <- extract.item(F2_fit, 6)
F3.item1 <- extract.item(F3_fit, 1)
F3.item2 <- extract.item(F3_fit, 2)
F3.item3 <- extract.item(F3_fit, 3)
F3.item4 <- extract.item(F3_fit, 4)
F3.item5 <- extract.item(F3_fit, 5)
F4.item1 <- extract.item(F4_fit, 1)
F4.item2 <- extract.item(F4_fit, 2)
F4.item3 <- extract.item(F4_fit, 3)
F4.item4 <- extract.item(F4_fit, 4)
F5.item1 <- extract.item(F5_fit, 1)
F5.item2 <- extract.item(F5_fit, 2)
F5.item3 <- extract.item(F5_fit, 3)
F5.item4 <- extract.item(F5_fit, 4)
F5.item5 <- extract.item(F5_fit, 5)

##Item Info
F1.item.info.1 <- iteminfo(F1.item1, Theta)
F1.item.info.2 <- iteminfo(F1.item2, Theta)
F1.item.info.3 <- iteminfo(F1.item3, Theta)
F2.item.info.1 <- iteminfo(F2.item1, Theta)
F2.item.info.2 <- iteminfo(F2.item2, Theta)
F2.item.info.3 <- iteminfo(F2.item3, Theta)
F2.item.info.4 <- iteminfo(F2.item4, Theta)
F2.item.info.5 <- iteminfo(F2.item5, Theta)
F2.item.info.6 <- iteminfo(F2.item6, Theta)
F3.item.info.1 <- iteminfo(F3.item1, Theta)
F3.item.info.2 <- iteminfo(F3.item2, Theta)
F3.item.info.3 <- iteminfo(F3.item3, Theta)
F3.item.info.4 <- iteminfo(F3.item4, Theta)
F3.item.info.5 <- iteminfo(F3.item5, Theta)
F4.item.info.1 <- iteminfo(F4.item1, Theta)
F4.item.info.2 <- iteminfo(F4.item2, Theta)
F4.item.info.3 <- iteminfo(F4.item3, Theta)
F4.item.info.4 <- iteminfo(F4.item4, Theta)
F5.item.info.1 <- iteminfo(F5.item1, Theta)
F5.item.info.2 <- iteminfo(F5.item2, Theta)
F5.item.info.3 <- iteminfo(F5.item3, Theta)
F5.item.info.4 <- iteminfo(F5.item4, Theta)
F5.item.info.5 <- iteminfo(F5.item5, Theta)

#Data frame

F1.item.info.data <- as.data.frame(cbind(Theta, F1.item.info.1, 
                                              F1.item.info.2,
                                              F1.item.info.3))

F2.item.info.data <- as.data.frame(cbind(Theta, F2.item.info.1, 
                                              F2.item.info.2,
                                              F2.item.info.3,
                                         F2.item.info.4,
                                         F2.item.info.5,
                                         F2.item.info.6))

F3.item.info.data <- as.data.frame(cbind(Theta, F3.item.info.1, 
                                              F3.item.info.2,
                                              F3.item.info.3,
                                         F3.item.info.4,
                                         F3.item.info.5))

F4.item.info.data <- as.data.frame(cbind(Theta, F4.item.info.1, 
                                              F4.item.info.2,
                                              F4.item.info.3,
                                         F4.item.info.4))
F5.item.info.data <- as.data.frame(cbind(Theta, F5.item.info.1, 
                                              F5.item.info.2,
                                              F5.item.info.3,
                                         F5.item.info.4,
                                         F5.item.info.5))

## GGplot2 item-info
###F1
F1.iteminfo.1 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.1)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item16") + geom_hline(yintercept = .20, colour ="red")
F1.iteminfo.2 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.2)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item36")+geom_hline(yintercept = .20, colour ="red")
F1.iteminfo.3 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.3)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item17")+ylim(0,6)+geom_hline(yintercept = .20, colour ="red")

###F2

F2.iteminfo.1 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.1)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F2 item11")+ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F2.iteminfo.2 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.2)) +
  geom_line()  + apatheme +
  labs(y="Item Information", title = "F2 item10")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F2.iteminfo.3 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.3)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F2 item12")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F2.iteminfo.4 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.4)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F2 item07")+ylim(0,3)+
  geom_hline(yintercept = .20, colour ="red")

F2.iteminfo.5 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.5)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F2 item08")+ylim(0,3)+
  geom_hline(yintercept = .20, colour ="red")

F2.iteminfo.6 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.6)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F2 item09")+ylim(0,3)+
  geom_hline(yintercept = .20, colour ="red")

###F3
F3.iteminfo.1 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.1)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F3 item27")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F3.iteminfo.2 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.2)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F3 item03")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F3.iteminfo.3 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.3)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F3 item40")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F3.iteminfo.4 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.4)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F3 item30")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F3.iteminfo.5 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.5)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F3 item41")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

#F4

F4.iteminfo.1 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.1)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F4 item32")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F4.iteminfo.2 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.2)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F4 item35")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F4.iteminfo.3 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.3)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F4 item38")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F4.iteminfo.4 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.4)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F4 item33")+geom_hline(yintercept = .20, colour ="red")

#F5

F5.iteminfo.1 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.1)) +
  geom_line()  +apatheme +labs(y="Item Information", title = "F5 item46")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F5.iteminfo.2 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.2)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F5 item45")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F5.iteminfo.3 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.3)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F5 item25")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

F5.iteminfo.4 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.4)) +
  geom_line()  +apatheme +
  labs(y="Item Information",title = "F5 item04")+
 geom_hline(yintercept = .20, colour ="red")

F5.iteminfo.5 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.5)) +
  geom_line()  +apatheme +
  labs(y="Item Information", title = "F5 item01")+
  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")

#Panel plots

F1.itemplots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F1.itemplots.png",F1.itemplots, width = 10, height = 12, dpi = 600,bg = "white")

F2.itemplots <- cowplot::plot_grid(F2.iteminfo.1,F2.iteminfo.2, F2.iteminfo.3,
                                   F2.iteminfo.4,F2.iteminfo.5,F2.iteminfo.6,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F2.itemplots.png",F2.itemplots, width = 10, height = 12, dpi = 600, bg = "white")

F3.itemplots <- cowplot::plot_grid(F3.iteminfo.1,F3.iteminfo.2, F3.iteminfo.3,
                                   F3.iteminfo.4,F3.iteminfo.5,
                 labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F3.itemplots.png",F3.itemplots, width = 10, height = 12, dpi = 600,bg = "white")

F4.itemplots <- cowplot::plot_grid(F4.iteminfo.1,F4.iteminfo.2, F4.iteminfo.3,
                                   F4.iteminfo.4,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F4.itemplots.png",F4.itemplots, width = 10, height = 12, dpi = 600,bg = "white")

F5.itemplots <- cowplot::plot_grid(F5.iteminfo.1,F5.iteminfo.2, F5.iteminfo.3,
                                   F5.iteminfo.4,F5.iteminfo.5,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 600, bg = "white")
```

@@

@@

# Person Fit ####
## F1 Person fit ####
F1.personfit <- personfit(F1_fit) 
F1.personfit_model_misfits <- subset(F1.personfit, Zh < -2)
rownames(F1.personfit_model_misfits)
nrow(F1.personfit_model_misfits)

F1.person <- ggplot(F1.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5,col=I("black"),fill=I("grey"))+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F1")+apatheme+ ylim(0,600) + xlim(-4,2)

## F2 Person fit ####
F2.personfit <- personfit(F2_fit.redu) 
F2.personfit_model_misfits <- subset(F2.personfit, Zh < -2)
rownames(F2.personfit_model_misfits)
nrow(F2.personfit_model_misfits)

F2.person <- ggplot(F2.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill=I("grey"))+
  scale_x_continuous(limits = c(-5, 1))+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F2")+apatheme+ylim(0,600) + xlim(-4,2)
